Ultra Diffuse Galaxies associated with Milky-Way Analogs

### 2022-08-30 main.tex
Updates from Overleaf

@@

\subsection{UDG and UPG sample}\label{sec:sample}
The UDG population is usually defined based on the surface brightness and the physical size of the galaxy. However, there are many different criteria in literature: \citep{vanDokkum2015} define UDGs to have effective radius $r_e$ larger than 1.5 kpc and central surface brightness $\mu_0(g)$ fainter than $24.0\ \sbunit$; other groups also use the surface brightness at $r_e$ \citep[e.g.,][]{DiCintio2017,Cardona-Barrero2020} or the average surface brightness within $r_e$ to define UDGs \citep[e.g.,][]{Koda2015,Yagi2016,vdBurg2016,Leisman2017,Martin2019}, and the size criterion also varies from $>1$ kpc to $>1.5$ kpc. \citet{vanNest2022} explore these definitions and find that different choice of UDG could drastically affect which subset of dwarfs are selected, therefore affect our understanding of the UDG population.

@@

We derive the stellar masses of galaxies in the UDG and UPG sample from the Spergel model fitting and a color-$M_{\star}/L$ relation from \citet{Into2013}:
\begin{align*}
&\log \left(M_{\star} / L_{g}\right)=1.774\,(g-r)-0.783, \\
&\log \left(M_{\star} / L_{g}\right)=1.297\,(g-i)-0.855.
\end{align*}
Because we have both $g-r$ and $g-i$ color available from the model fitting, we use the average of the $M_{\star}/L$ derived from the two colors for calculating stellar mass. We assume the solar absolute magnitude in $g$-band to be 5.03 \citep{Willmer2018}. We correct for the effect of Galactic extinction on colors based on \citet{SFD1998,Schlafly2011}. The magnitudes and surface brightnesses are also extinction-corrected.

@@

One of the main goals of this paper is to study the star-forming properties of UDGs and UPGs in MW analogs. The star formation rate of galaxies is indicated by broad-band colors, and we use color to calculate the quenched fraction of UDGs and UPGs. However, background contaminants affect the color distribution of the UDG (UPG) sample, thus affect the calculated quenched fraction. If the fake UDGs (UPGs) span a different region from the true UDGs in the observable space, we can use these observables to assign weights to each object in our UDG sample indicating the possibility of being a true UDG. Indeed, we find that the $g-i$ color distribution of the fake UDG sample is bluer than that of the true UDG sample, which motivates us to assign importance weights based on $g-i$ color. We first compute the normalized histograms of $g-i$ colors (denoted as $\lambda_k$ at $(g-i)_{k}$ bins) for both true UDG and fake UDG samples. Then we multiply $f_{\rm contam}$ with the histogram of fake UDG sample ($\lambda_k^{\rm fake}$) such that the histogram sums up to the average contamination fraction. The weights of UDGs in color bin $(g-i)_k$ is estimated to be $w_k = \max\,(1 - f_{\rm contam} \lambda_k^{\rm fake} / \lambda_k^{\rm true}, 0)$. This weight stands for a possibility of being a contaminant. The weights of UPGs are assigned following the same procedure. We find this color-based contamination subtraction scheme is sufficient for this work since the contamination fraction is small. Our main results aren shown in Section \ref{sec:results} are robust against contamination subtraction.

\section{Results}\label{sec:results}
In this section, we present statistical analysis of UDGs and UPGs associated with MW analogs in the nearby Universe. TLDR the full section here?

\subsection{UDG and UPG on mass-size plane}

\begin{figure*}
	\vbox{ 
		\centering
		\includegraphics[width=1\linewidth]{mass_size_plane.pdf}
	}
    \caption{The distributions of the UDG and UPG sample on the mass-size plane. The data points are color-coded by the distance to the quenching color cut. Squares are those galaxies satisfying both UDG and UPG definition, stars (triangles) are those only satisfying UDG (UPG) definition.
    We plot the average mass-size relation (light green) and $1.5\sigma$ above the average relation (dark green) as dashed lines for reference. In the left panel, we show the constant surface brightness line as solid lines by assuming two different $g-i$ colors. Galaxies falling between these two lines are mostly red and quenched because blue UDGs have too be very large in size to satisfy the surface brightness criterion. This hard surface brightness cut makes the UDG quenched fraction high. 
    }
    \label{fig:mass_size}
\end{figure*}

\subsection{Abundance of UDGs and UPGs}\label{sec:n_udg}
\jiaxuan{Discuss NGVS}
\begin{figure*}
	\vbox{ 
		\centering
		\includegraphics[width=1\linewidth]{N_UDG_host_mass.pdf}
	}
    \caption{The abundance of UDGs as a function of host halo mass. \textit{Left}: We compile the UDG abundance measurements from literature covering a wide range of host mass. The UDG abundance of our work $N_{\rm UDG} = 0.76\pm 0.04$ is shown as red square, the power-law relation from \citet{vdBurg2017} is shown in gray, and our fitting result is shown in pink. Our UDG abundance is consistent with ELVES but significantly higher than that in SAGA. After including more measurements at the lower halo mass end, the power-law is shallower than the relation reported in \citet{vdBurg2017}. \textit{Right}: We split the UDG sample into bins based on the host halo mass (triangles) and $g-i$ color (pentagons). The UDG abundance is higher for more massive host and redder host. }
    \label{fig:n_udg}
\end{figure*}

As demonstrated by many previous studies \citep[e.g.,][]{vdBurg2016,vdBurg2017}, the average number of UDGs per host scales with host halo mass. While much literature focuses on finding UDGs in clusters and large groups, there are fewer constraints on the UDG abundance at the lower halo mass end. In this section, we calculate the UDG abundance of MW analogs, and compare with other surveys.

We define the UDG abundance as the average number of UDGs per host galaxy. In our UDG sample, there are 412 UDGs associated with 258 hosts. After correcting for background contamination (see Section \ref{sec:bkg}) and completeness (see Section \ref{sec:completeness}), the UDG abundance of MW analogs is $N_{\rm UDG} = 0.76\pm 0.04$ per host. Here we neglect the fact that the number of satellites contained within the virial sphere is different from the number of satellite within a projected cylinder with virial radius (the so-called deprojection factor, \citealt{vdBurg2017}).

We compare our UDG abundance with other surveys focused on MW analogs. In the SAGA survey \citep{SAGA-II}, 6 satellite galaxies (out of 127 spectroscopy-confirmed satellites around 36 MW analogs) satisfy the definition of UDG. Therefore the UDG fraction in \citet{SAGA-II} is about $N_{\rm UDG,\, SAGA} \approx 0.17\pm0.07$. In the ELVES survey \citep{CarlstenELVES2022}, there are 15 satellites (out of 404 satellites associated with 30 MW analogs) satisfying the UDG definition, leading to a UDG fraction of $N_{\rm UDG,\, ELVES} \approx 0.50\pm0.13$. \citet{Roman2017b} identified 11 UDGs around three galaxy groups in the IAC Stripe 82 Legacy Survey \citep{Fliri2016}. Since both SAGA and ELVES select satellites based on distance measurements and do not correct for completeness, their UDG abundances are interpreted as lower limits. \citet{Roman2017b} do not estimate the background contamination fraction and do not correct for completeness either. We plot the UDG abundances of these surveys in the left panel of Figure \ref{fig:n_udg}, together with the results for larger galaxy groups and clusters \citep{Koda2015,Munoz2015,Roman2017a,Roman2017b,Janssens2017,vdBurg2017}. Among these studies, only \citet{vdBurg2017} applies a background subtraction and completeness correction to the raw counts. The power-law regression result from \citet{vdBurg2017} $N_{\rm UDG} \propto M_h^{1.11\pm 0.07}$ is shown in gray. The UDG abundance of this work is highlighted as the red square. As shown in Figure \ref{fig:n_udg}, the scatter in the $N_{\rm UDG}-M_h$ relation gets larger at the lower halo mass end. Our UDG abundance is similar to the value in ELVES survey, but is marginally higher than the prediction from \citet{vdBurg2017} although still consistent within the scatter. The UDG abundances from SAGA are significantly lower than both ELVES and our result. This might be explained by the different photometric depth of data used. SAGA selects dwarf candidates in DECaLS data, which is x mag shallower than the CFTH and HSC data used in ELVES and this work. It is probable that SAGA missed a significant fraction of red and lower surface brightness galaxies.

Taking all data points from literature (as shown in Figure \ref{fig:n_udg}), we use orthogonal distance regression (ODR) to fit a power-law between $N_{\rm UDG}$ and host halo mass $M_h$ and find $N_{\rm UDG} \propto M_h^{0.96\pm 0.04}$, shown as the pink dashed line in Figure \ref{fig:n_udg}. The slope of the power law is shallower than \citet{vdBurg2017} ($\beta=1.11\pm0.07$) but still steeper than \citet{Roman2017b} ($\beta=0.85\pm0.05$). Since most individual studies do not have a statistical estimation for background contamination and completeness, the UDG abundances for large groups should be interpreted as lower limits. If completeness is applied, it is possible that the slope $\beta$ will be steeper than what we are showing in Figure \ref{fig:n_udg}.

In the right panel, we split the UDG sample into different bins based on their host halo mass (shown as triangles) and host color (shown as pentagons). The UDG abundance is slightly higher for hosts with higher halo mass and redder color, but the trend is stronger with host color.

\citet{Liao2019} also shows a shallower power law with 0.93. We can add that paper here.

\jiaxuan{UPG abundances, and compare with UDGs}

quenched line: Meng's manga paper. color-mass.

% Plot the UDG and UPG population on the re-abs mag plane (Bovy book)
% \citet{Trujillo2020}: define size based on surface mass density
% We correct for completeness after statistical contamination subtraction.

\subsection{Size distribution}\label{sec:size_distr}
\jiaxuan{Plot size distribution in two radial bins, to test whether tidal stripping prevails ram pressure stripping. }
\begin{figure*}
	\vbox{ 
		\centering
		\includegraphics[width=1\linewidth]{size_distribution.pdf}
	}
    \caption{Caption}
    \label{fig:size_distribution}
\end{figure*}

@@

\jiaxuan{vdb17 doesn't estimate measurement bias.}

We find that the UDG size distribution roughly follows a power law. We fit a power law relation to our UDG size distribution and get $n\propto r_e^{-1.60\pm0.21}$. This is shallower than the power law presented in \citet{vdBurg2016} ($n\propto r_e^{-3.40\pm0.19}$) and \citet{vdBurg2017} ($n\propto r_e^{-2.71\pm0.33}$, shown as gray dash-dotted lines in Figure \ref{fig:size_distribution}). We also split the UDG sample based on their host stellar mass, but consistently find shallow power-laws with index $\sim -1.6$. \citet{vdBurg2016} studies large galaxy clusters and find a very steep slope, \citet{vdBurg2017} includes less-massive groups and the slope is less steep. Combined with our findings, it might be possible that dense environment produces more small UDGs. \jiaxuan{Have anything to do with tidal stripping? UDGs in denser environs are more stripped thus smaller?}

@@

Since the discovery of UDGs in Coma cluster, the radial distribution of UDGs around the hosts has been a valuable tool to test various UDG formation theories (cite simulation papers). In \citet{vanDokkum2015}, UDGs are not found within 300 kpc from the cluster center, hinting that UDGs might not survive in such a dense environment. \citet{vdBurg2016} has also found that the number of UDGs is suppressed near the center of clusters, and the radial distribution of UDGs in cluster environments roughly follows a projected Einasto \citep{Einasto1965} profile. In the following, we derive the radial distribution of UDGs and UPGs in our sample and discuss possible implications.

@@

We don't discriminate our hosts to be paired or not.

@@

% lower-mass satellites are mostly quiescent, roughly half of intermediate-mass satellites are quiescent, and higher-mass satellites are mostly star-forming

\jiaxuan{TODO: make data products (catalogs, fake UDGs, website for their images, etc.)}

@@

\subsection{High and constant quenched fraction of UDGs is an artifact}
In Section \ref{sec:quench}, we calculate the quenched fraction as a function of stellar mass for UDGs (left panels in Figure \ref{fig:qfrac}). We find that the UDG quenched fraction is reasonably a constant over $>1$ dex in stellar mass, and is higher than the quenched fractions of UPGs and satellite population of MW analogs. In this subsection, we argue that UDG's high and constant quenched fraction is merely an artifact due to its contrived definition.

In Figure \ref{fig:mass_size}, we plot our UDG sample on the mass-size plane. Because we use a color cut $(g-i)_{Q} = -0.067 M_V - 0.23$ to define quenching, we define $\Delta(\mathrm{Quench}) = (g-i) - (g-i)_{Q}$ as an indicator for how much it has been quenched. Higher $\Delta(\mathrm{Quench})$ means that the galaxy is actively star-forming, whereas smaller $\Delta(\rm Quench)$ indicates the galaxy has been quenched more. The data points in Figure \ref{fig:mass_size} are color-coded by this $\Delta(\mathrm{Quench})$. As shown as green dashed lines, we plot the mass-size relation (and $1.5\sigma$ above the mean mass-size relation) derived from the satellite systems of MW analogs in Local Volume \citep{ELVES-I}. The two solid lines correspond to the surface brightness cut at $\sbeff = 25.0\ \sbunit$ by assuming different colors. For the redshift range of our sample, the surface brightness is a constant with distance since the cosmological effect is negligible.

UDG with a redder color has a higher mass-to-light ratio, thus for a given mass and surface brightness, its size is smaller than a blue UDG. Consequently, only those large blue UDGs can satisfy the UDG definition. As shown in the left panel of Figure \ref{fig:mass_size}, galaxies between the red and the blue solid lines are mostly quenched ($\Delta(\mathrm{Quench}) < 0$). Due to the color-M/L relation, a fixed surface brightness cut makes red galaxies dominate the UDG population at the smaller size end, and thus giving rise to a high quenched fraction as we see in Figure \ref{fig:qfrac}.

The UPGs are defined as those galaxies at $1.5\sigma$ above the average mass-size relation. The right panel of Figure \ref{fig:mass_size} shows their distribution on mass-size plane. The squares are those galaxies classified as both UDG and UPG, stars are objects that are classified as UDG only, and triangles are UPGs only. We see a lot of blue galaxies with large size classified only as UPG because their surface brightness is too high to satisfy the UDG definition.

% We recall that the UDG is defined to have $r_e > 1.5$ kpc and $\mu_0(g) > 24.0\ \sbunit$ (or equivalently $\sbeff > 25.0\ \sbunit$).

@@

Dwarf galaxy: most of them are blue in field, and most satellites of MW and larger groups/clusters are quenched. Among others, tidal stripping and ram-pressure stripping are thought to quench the satellites.

@@

We compare with SAGA quenched fraction (Mao) and ELVES (Carlsten, Greene in prep).

@@

SAGA misses a fraction of red faint galaxies in their intial detection catalogs. This also explains the low quenched fraction of SAGA \citep{CarlstenELVES2022}.
SAGA SB limit is 25. ARTEMIS is able to reproduce SAGA quenched fraction.

\subsection{UDG and UPG formation}
In this paper, one surprising finding is that although UPGs have extremely large size for their stellar mass, they have similar quiescent fraction as normal satellites in MW analogs. In ELVES, \citet{ELVES-I} find that the mass-size relation of satellites in MW analogs does not depend on the morphology (equivalently color) of satellites. They interpret this trend as that the quenching and morphological transformation involves very mild size evolution. These evidences might indicate that quenching and size growth must happen separately. Then the question is what physics is responsible for the two processes respectively. In this section, we first review the quenching of MW satellites and the mechanisms for puffing up normal dwarfs to produce UDGs (UPGs). Then we combine the results presented in Section \ref{sec:results} and discuss possible implications on the formation and quenching of UDGs and UPGs. 
\footnote{\jiaxuan{Greene et al. (in prep) also find no trend of quenched fraction on the size?}}

>>>>

Stellar population of UDGs \citep[e.g.,][]{Gu2018}

@@

\subsection{UDG and UPG sample}\label{sec:sample}
\jiaxuan{TODO: make data products (catalogs, fake UDGs, website for their images, etc.)}

The UDG population is usually defined based on the surface brightness and the physical size of the galaxy. However, there are many different criteria in literature: \citep{vanDokkum2015} define UDGs to have effective radius $r_e$ larger than 1.5 kpc and central surface brightness $\mu_0(g)$ fainter than $24.0\ \sbunit$; other groups also use the surface brightness at $r_e$ \citep[e.g.,][]{DiCintio2017,Cardona-Barrero2020} or the average surface brightness within $r_e$ to define UDGs \citep[e.g.,][]{Koda2015,Yagi2016,vdBurg2016,Leisman2017,Martin2019}, and the size criterion also varies from $>1$ kpc to $>1.5$ kpc. \citet{vanNest2022} explore these definitions and find that different choice of UDG could drastically affect which subset of dwarfs are selected, therefore affect our understanding of the UDG population.

@@

We derive the stellar masses of galaxies in the UDG and UPG sample from the Spergel model fitting and a relation between color and mass-to-light ratio $M_{\star}/L$ from \citet{Into2013}:
\begin{align*}
&\log \left(M_{\star} / L_{g}\right)=1.774\,(g-r)-0.783, \\
&\log \left(M_{\star} / L_{g}\right)=1.297\,(g-i)-0.855.
\end{align*}
Because we have both $g-r$ and $g-i$ color available from the model fitting, we use the average of the $M_{\star}/L$ derived from the two colors for calculating stellar mass. We assume the solar absolute magnitude in $g$-band to be 5.03 \citep{Willmer2018}. We correct for the effect of Galactic extinction on colors based on \citet{SFD1998,Schlafly2011}. The magnitudes and surface brightnesses are also extinction-corrected.

@@

One of the main goals of this paper is to study the star-forming properties of UDGs and UPGs in MW analogs. The star formation rate of galaxies is indicated by broad-band colors, and we use color to calculate the quenched fraction of UDGs and UPGs. However, background contaminants affect the color distribution of the UDG (UPG) sample, thus affect the calculated quenched fraction. If the fake UDGs (UPGs) span a different region from the true UDGs in the observable space, we can use these observables to assign weights to each object in our UDG sample indicating the possibility of being a true UDG. Indeed, we find that the $g-i$ color distribution of the fake UDG sample is bluer than that of the true UDG sample, which motivates us to assign importance weights based on $g-i$ color. We first compute the normalized histograms of $g-i$ colors (denoted as $\lambda_k$ at $(g-i)_{k}$ bins) for both true UDG and fake UDG samples. Then we multiply $f_{\rm contam}$ with the histogram of fake UDG sample ($\lambda_k^{\rm fake}$) such that the histogram sums up to the average contamination fraction. The weights of UDGs in color bin $(g-i)_k$ is estimated to be $w_k = \max\,(1 - f_{\rm contam} \lambda_k^{\rm fake} / \lambda_k^{\rm true}, 0)$. This weight stands for a possibility of being a contaminant. The weights of UPGs are assigned following the same procedure. We find this color-based contamination subtraction scheme is sufficient for this work since the contamination fraction is small. Our main results shown in Section \ref{sec:results} are robust against contamination subtraction.

We note that we do not apply any background correction in Fig. \ref{fig:size_distribution} and Fig. \ref{fig:mass_size}.

\section{Results}\label{sec:results}
In this section, we present statistical analysis of UDGs and UPGs associated with MW analogs in the nearby Universe.

\subsection{UDG and UPG on the mass-size plane}\label{sec:mass-size}
\begin{figure*}
	\vbox{ 
		\centering
		\includegraphics[width=1\linewidth]{mass_size_plane.pdf}
	}
    \caption{The distributions of the UDG and UPG sample on the mass-size plane. The data points are color-coded by the distance to the quenching color cut. Squares are those galaxies satisfying both UDG and UPG definition, stars (triangles) are those only satisfying UDG (UPG) definition.
    We plot the average mass-size relation (light green) and $1.5\sigma$ above the average relation (dark green) as dashed lines for reference. In the left panel, we show the constant surface brightness line as solid lines by assuming two different $g-i$ colors. Galaxies falling between these two lines are mostly red and quenched because blue UDGs have too be very large in size to satisfy the surface brightness criterion. This hard surface brightness cut makes the UDG quenched fraction high. 
    }
    \label{fig:mass_size}
\end{figure*}

In order to build a more comprehensive intuition on our UDG and UPG sample, we show their distributions on the mass-size plane in Figure \ref{fig:mass_size}. In the left panel, UDGs that are also classified as UPGs are shown in squares, while UDGs that do not satisfy UPG criteria are marked as stars. In the right panel, triangles correspond to UPGs that are not classified as UDGs. To orient us on the mass-size plane, we display the average mass-size relation derived from the satellites of MW analogs in the Local Volume \citep{ELVES-I} as the light green dashed lines. The darker green line shows $1.5\sigma$ above the average mass-size relation assuming the scatter of the mass-size relation to be $\sigma=0.181$ dex \citep{ELVES-I}. Because UDGs are defined to have $r_e > 1.5$ kpc and $\sbeff > 25.0\ \sbunit$, we see a hard cut on size and surface brightness in the left panel. In the right panel, we see that UPGs are all above the $1.5\sigma$ line by construction. Comparing the two panels, we find that the UDG sample includes a number of galaxies below $1.5\sigma$ line (highlighted as stars), but also lose a few low-mass galaxies with sizes smaller than 1.5 kpc. UDGs below $1.5\sigma$ line have sizes larger than 1.5 kpc, but not large enough given their masses. It is also noticeable that UPG sample has a few galaxies with $M_\star > 10^{8.5}\ M_\odot$ which have surface brightness brighter than $25.0\ \sbunit$. As a consequence, the size distribution of UPGs at the smaller end is suppressed as shown in Fig. \ref{fig:size_distribution}.

As we will introduce in Section \ref{sec:quench}, we use a color cut $(g-i)_{Q}$ to separate galaxies with active star formation from quiescent ones. Here we define $\Delta(\mathrm{Quench}) = (g-i) - (g-i)_{Q}$ as an indicator for how much it has been quenched. Higher $\Delta(\mathrm{Quench})$ indicates that the galaxy is actively star-forming, whereas smaller $\Delta(\rm Quench)$ means the galaxy has lower star formation rate. We color-code the galaxies in Figure \ref{fig:mass_size} with $\Delta(\mathrm{Quench})$. UDGs below the $1.5\sigma$ line have near zero or negative $\Delta(\mathrm{Quench})$, implying that the UDG sample includes plenty of quenched galaxies compared with the UPG sample. Instead, the UPG sample is comprised of many star-forming galaxies at the high-mass end.

In Fig. \ref{fig:mass_size}, we also show constant surface brightness lines in the left panel and constant mass surface density in the right panel. We will discuss how the definition of UDG could bias the quenched fraction later in Sec. \ref{sec:discussion}.

\jiaxuan{@Jenny: any other things to mention in this section?}

\subsection{Abundance of UDGs and UPGs}\label{sec:n_udg}

\begin{figure*}
	\vbox{ 
		\centering
		\includegraphics[width=1\linewidth]{N_UDG_host_mass.pdf}
	}
    \caption{The abundance of UDGs as a function of host halo mass. \textit{Left}: We compile the UDG abundance measurements from literature covering a wide range of host mass. The UDG abundance of our work $N_{\rm UDG} = 0.76\pm 0.04$ is shown as red square, the power-law relation from \citet{vdBurg2017} is shown in gray, and our fitting result is shown in pink. Our UDG abundance is consistent with ELVES but significantly higher than that in SAGA. After including more measurements at the lower halo mass end, the power-law is shallower than the relation reported in \citet{vdBurg2017}. \textit{Right}: We split the UDG sample into bins based on the host halo mass (triangles) and $g-i$ color (pentagons). The UDG abundance is higher for more massive host and redder host. }
    \label{fig:n_udg}
\end{figure*}

As demonstrated by many previous studies \citep[e.g.,][]{vdBurg2016,vdBurg2017,Roman2017a}, the average number of UDGs per host scales with host halo mass. While much literature focuses on finding UDGs in clusters and large groups, there are fewer constraints on the UDG abundance at the lower halo mass end. In this section, we calculate the UDG abundance of MW analogs, and compare with other surveys.

We define the UDG (UPG) abundance as the average number of UDGs (UPGs) per host galaxy. In our UDG sample, there are 412 UDGs associated with 258 hosts. After correcting for background contamination (see Section \ref{sec:bkg}) and completeness (see Section \ref{sec:completeness}), the UDG abundance of MW analogs is $N_{\rm UDG} = 0.76\pm 0.04$ per host. The UPG abundance in our sample is $N_{\rm UPG} = 0.61\pm 0.04$ per host. Here we neglect the fact that the number of satellites contained within the virial sphere is different from the number of satellite within a projected cylinder with virial radius (the so-called deprojection factor, \citealt{vdBurg2017}).

We compare our UDG abundance with other surveys focused on MW analogs. In the SAGA survey \citep{SAGA-II}, 6 satellite galaxies (out of 127 spectroscopy-confirmed satellites around 36 MW analogs) satisfy the definition of UDG. Therefore the UDG abundance in \citet{SAGA-II} is about $N_{\rm UDG,\, SAGA} \approx 0.17\pm0.07$. In the ELVES survey \citep{CarlstenELVES2022}, there are 15 satellites (out of 404 satellites associated with 30 MW analogs) satisfying the UDG definition, leading to a UDG abundance of $N_{\rm UDG,\, ELVES} \approx 0.50\pm0.13$. \citet{Roman2017b} identified 11 UDGs around three galaxy groups in the IAC Stripe 82 Legacy Survey \citep{Fliri2016}. Since both SAGA and ELVES select satellites based on distance measurements and do not correct for completeness, their UDG abundances are interpreted as lower limits. \citet{Roman2017b} do not estimate the background contamination fraction and do not correct for completeness either. We plot the UDG abundances of these surveys in the left panel of Figure \ref{fig:n_udg}, together with the results for larger galaxy groups and clusters \citep{Koda2015,Munoz2015,Roman2017a,Roman2017b,Janssens2017,vdBurg2017}. Among these studies, only \citet{vdBurg2017} applies a background subtraction and completeness correction to the raw counts.  In the Auriga simulations, \citet{Liao2019} find $N_{\rm UDG,\ Auriga}=1.27\pm 1.06$ for UDGs in MW-mass hosts. The power-law regression result from \citet{vdBurg2017} $N_{\rm UDG} \propto M_h^{1.11\pm 0.07}$ is shown in gray. The UDG abundance of this work is highlighted as the red square. As shown in Figure \ref{fig:n_udg}, the scatter in the $N_{\rm UDG}-M_h$ relation gets larger at the lower halo mass end. Our UDG abundance is similar to the value in ELVES survey, but is marginally higher than the prediction from \citet{vdBurg2017} although still consistent within the scatter. The UDG abundances from SAGA are significantly lower than both ELVES and our result. This might be explained by the different photometric depth of data used. As pointed out by \citet{CarlstenELVES2022,Font2022}, SAGA survey reaches a surface brightness depth of $\sbeffr\approx 25\ \sbunit$, which is $\sim 2.5\ \sbunit$ shallower than the ELVES survey and this work. It is probable that SAGA missed a significant fraction of red and lower surface brightness galaxies.

Taking all data points from literature (as shown in Figure \ref{fig:n_udg}), we use orthogonal distance regression (ODR) to fit a power-law between $N_{\rm UDG}$ and host halo mass $M_h$ and find $N_{\rm UDG} \propto M_h^{0.96\pm 0.04}$, shown as the pink dashed line in Figure \ref{fig:n_udg}. The slope of the power law is shallower than \citet{vdBurg2017} ($\beta=1.11\pm0.07$) but still steeper than \citet{Roman2017b} ($\beta=0.85\pm0.05$). Since most individual studies do not have a statistical estimation for background contamination and completeness, the UDG abundances for large groups should be interpreted as lower limits. If completeness is applied, it is possible that the slope $\beta$ will be steeper than what we are showing in Figure \ref{fig:n_udg}. We also note that many studies do no consider measurement bias and uncertainty, which makes the comparisons more difficult.

In the right panel of Figure \ref{fig:n_udg}, we split the UDG sample into different bins based on their host halo mass (shown as triangles) and host color (shown as pentagons). The UDG abundance is slightly higher for hosts with higher halo mass and redder color, but the trend is stronger with host color.

Another interesting quantity is the fraction of UDGs (UPGs) out of all satellites in a group or cluster. We denote this fraction as UDG (UPG) fraction hereafter, which characterizes the tail of the size distribution of satellites. In order to calculate this fraction, we assume that MW analogs have $\sim 5$ satellites with $M_\star > 10^{6.5}\ M_\odot$ \citep{CarlstenELVES2022}. This lower limit of stelalr mass is roughly our detection limit (see Fig. \ref{fig:mass_size}). Then for our samples, the UDG (UPG) fraction is $f_{\rm UDG} \approx 0.15$ and $f_{\rm UPG} \approx 0.12$. We compare our results with the Virgo cluster. Taking the data from the Next Generation Virgo Cluster Survey (NGVS, \citealt{Ferrarese2020}), there are 15 UDGs and 24 UPGs out of 404 identified satellites without completeness correction. Thus their UDG (UPG) fraction is $f_{\rm UDG,\  Virgo}=0.04$ and $f_{\rm UPG,\ Virgo} = 0.06$. However, we note that \citet{Ferrarese2020} only survey the central 4 deg$^2$ of the Virgo cluster, which probably biases the UDG (UPG) fraction. A more systematic comparison on UDG (UPG) fraction in different environments is needed in the future.

\subsection{Size distribution}\label{sec:size_distr}

\begin{figure*}
	\vbox{ 
		\centering
		\includegraphics[width=1\linewidth]{size_distribution.pdf}
	}
    \caption{Caption}
    \label{fig:size_distribution}
\end{figure*}

@@

We find that the UDG size distribution roughly follows a power law. We fit a power law relation to our UDG size distribution and get $n\propto r_e^{-1.60\pm0.21}$. This is shallower than the power law presented in \citet{vdBurg2016} ($n\propto r_e^{-3.40\pm0.19}$) and \citet{vdBurg2017} ($n\propto r_e^{-2.71\pm0.33}$, shown as gray dash-dotted lines in Figure \ref{fig:size_distribution}). We also split the UDG sample based on their host stellar masses and also distance to their hosts, but consistently find shallow power-laws with index $\sim -1.6$. In particular, we do not find significant change in the size distribution as UDGs (UPGs) get closer to their hosts. \citet{vdBurg2016} studies large galaxy clusters and find a very steep slope, \citet{vdBurg2017} includes less-massive groups and the slope is less steep. Combined with our findings, it might be possible that dense environment produces more smaller UDGs. As we will discuss in Sec. \ref{sec:discussion}, cluster environments provide stronger tidal fields and thus are more efficient on producing large UDGs due to tidal heating.

@@

Since the discovery of UDGs in Coma cluster, the radial distribution of UDGs around the hosts has been a valuable tool to test various UDG formation theories (cite simulation papers). In \citet{vanDokkum2015}, UDGs are not found within 300 kpc from the cluster center, hinting that UDGs might not survive in such a dense environment. \citet{vdBurg2016} has also found that the number of UDGs is suppressed near the center of clusters, and the radial distribution of UDGs in cluster environments roughly follows a projected Einasto profile \citep{Einasto1965}. In the following, we derive the radial distribution of UDGs and UPGs in our sample and discuss possible implications.

@@

@@

% lower-mass satellites are mostly quiescent, roughly half of intermediate-mass satellites are quiescent, and higher-mass satellites are mostly star-forming
% the satellites in MW analogs are mostly quiescent below $M_\star\approx 10^7\ M_\odot$, and the quenched fraction drops as increasing stellar mass.

@@

\subsection{High and constant quenched fraction of UDGs is an artifact}
In Section \ref{sec:quench}, we calculate the quenched fraction as a function of stellar mass for UDGs (left panels in Figure \ref{fig:qfrac}). We find that the quenched fraction of UDGs is higher than the quenched fractions of UPGs and the satellite population of MW analogs. Furthermore, it remains a constant over $>1$ dex in stellar mass. In this subsection, we argue that UDG's high and constant quenched fraction is merely an artifact due to its contrived definition. We also discuss the advantages and disadvantages of different definitions of low surface brightness galaxies.

In Figure \ref{fig:mass_size}, we show our UDGs and UPGs on the mass-size plane color-coded by $\Delta(\mathrm{Quench})$ indicating how much a galaxy has been quenched. As we described in Section \ref{sec:mass-size}, the UDG sample includes a number of galaxies below the $1.5\sigma$ mass-size line. Additionally, these galaxies are mostly quenched (having zero or negative $\Delta(\mathrm{Quench})$). In order to help understand this phenomenon, we plot constant surface brightness lines of $\sbeff=25.0\ \sbunit$ for two different colors $g-i=0.4$ (blue solid line) and $g-i=0.8$ (red solid line). For our redshift range, the cosmological dimming effect is negligible and the surface brightness is a constant with distance. For a given size, surface brightness (e.g., $\sbeff=25.0\ \sbunit$), redder galaxies have the same absolute magnitude as blue galaxies, but have larger stellar mass because they have larger mass-to-light ratio than blue galaxies. The mass-to-light ratio effect manifests itself on Figure \ref{fig:mass_size} by separating the two constant surface brightness lines apart. We recall that the UDG is defined to have $r_e > 1.5$ kpc and $\sbeff > 25.0\ \sbunit$. As a result of the color-M/L relation, the UDG sample includes more red galaxies than blue ones by having a surface brightness cut at $\sbeff=25.0\ \sbunit$, and thus give rise to a high quenched fraction as we see in Figure \ref{fig:qfrac}. It is the pathological definition of UDG that makes the quenched fraction high.

We note that the color-$M_\star/L$ relation are only invoked when converting the absolute magnitude to stellar mass. Thus when studying the quenched fraction as a function of absolute magnitudes, the dependence of

one will 't see a high and constant quenched fraction for UDGs.

@@

Dwarf galaxy: most of them are blue in field, and most satellites of MW and larger groups/clusters are quenched.

@@

@@

SAGA misses a fraction of red faint galaxies in their initial detection catalogs. This also explains the low quenched fraction of SAGA \citep{CarlstenELVES2022}.
SAGA SB limit is 25. ARTEMIS is able to reproduce SAGA quenched fraction.

\jiaxuan{UPG help us define mass-size lognormal, more diverse environment. distances.}

\citet{Trujillo2020}: define size based on surface mass density

\subsection{UDG and UPG formation}
In this paper, one surprising finding is that although UPGs have extremely large size for their stellar mass, they have similar quiescent fraction as normal satellites in MW analogs. In ELVES, Greene et al. (in prep) also find no trend of quenched fraction on size. \citet{ELVES-I} find that the mass-size relation of satellites in MW analogs does not depend on the morphology (equivalently color) of satellites, suggesting that the quenching and morphological transformation involves very mild size evolution. Perhaps quenching and size growth happen separately. Then the question is what physics is responsible for the two processes respectively. In this section, we first review the quenching of MW satellites and the mechanisms for puffing up normal dwarfs to produce UDGs (UPGs). Then we combine the results presented in Section \ref{sec:results} and discuss possible implications on the formation and quenching of UDGs and UPGs.

%%%%%%%%%%%%%%%%%%%
Isolated dwarf galaxies in the field are known to be star-forming \citep{Geha2012}, but satellites in the Local Group and Local Volume are more quiescent \citep{Grcevich2009,Spekkens2014,Wetzel2015,Putman2021,CarlstenELVES2022}. This difference hints that the MW environments play an important role in regulating the star formation activities in dwarf galaxies. There have been extensive works using simulations to study the quenching of satellites in MW analogs \citep[e.g.,][]{Simpson2018,Buck2019,Garrison-Kimmel2019,Simons2020,Joshi2021,Akins2021,Karunakaran2021,Font2022,Samuel2022}, and many of them are able to reproduce the observed quenched fraction in the Local Group and in the Local Volume.
